Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-02 paper/main.tex
deform retract + figuring out artist

% *** MATH PACKAGES ***
%% with other math-related packages, you may want to disable it.
\usepackage{amsmath, amsthm, amsfonts,amssymb,eulervm,xspace, mathtools}
\usepackage{mathrsfs} % math script fonts
\usepackage{bm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\newtheorem{example}{Example}[section]
% *** SPECIALIZED LIST PACKAGES ***
\usepackage{xcolor}
\usepackage{algorithmic}
\usepackage[utf8]{inputenc}
\usepackage{subfig} %ieee does not like subfigure
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?
\usepackage[switch]{lineno}
\renewcommand{\linenumberfont}{\normalfont\bfseries\small\color{lightgray}}
\usepackage{minted}
\setminted[python]{fontsize=\scriptsize, 
                   linenos,
                   numbersep=8pt,
                   autogobble, 
                   frame=lines,
                   framesep=3mm} 
% *** ALIGNMENT PACKAGES ***
\usepackage{array}
\usepackage{tabulary}
% IEEEtran contains the IEEEeqnarray family of commands

@@

\subsection{Sheaves}
Sheaves can be thought of as an "algebraic data structure" \cite{ghristElementaryAppliedTopology2014} for data that lives over topological spaces. A presheaf $\sheafc$ is a map from the open set to the set of sections $\sheafc: \opensetc \rightarrow \cgamma{\opensetc}{ \dtotalc|_{\opensetc}}$ \cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf}. The presheaf preserves inclusion maps $\iota$ between open sets and the inclusion map $\iota^*$ between the sets of sections.

@@

We introduce the category $\mathcal{\dbase}$ to encapsulate the subsets of the continuity and the inclusion maps that glue them together.

\begin{definition} \label{def:category:K} The category of open sets $\mathcal{\dbasec}$ consists of
  \begin{itemize}
    \item \textit{objects} open sets $\openset_{i} \in \{\openset\}$ in the topological space $(\dbase, \mathscr{T})$), including the empty set $\varnothing$ and the maximum set \dbase. 
    \item \textit{morphisms} $\iota: \openset_{i} \hookrightarrow \openset_{j}$ for all  $\openset_i, \openset_j \subset \dtotal$
  \end{itemize} 
\end{definition}

We model a space of data sets with the same continuity and fields as the sheaf  $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$.
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc}{\dtotalc|_{\opensetc}} \in Ob(\setc) & \\
    {} & & {} \\
    & \opensetc \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)"', shift left = 10, color=sheaf] &   
\end{tikzcd}
\end{equation}
The objects of \textbf{Set} in this sheaf are the sets of sections $\Gamma(\dbase, \dtotal)$ introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps $(\iota, \iota^*)$ introduced in \autoref{eq:related-work:continuity:presheaf}. As mentioned in \autoref{re} sections $\dsection$ are

\note{add transition sentence about artist }

The continuity of the graphic is encapsulated as a category $\mathcal{\gbase}}$

\begin{definition} The category of open sets $\mathcal{\gbase}$ in the topological space $(\dbase, \mathscr{T})$). This category consists of open set \textit{objects} $\opensetg \in \{\opensetg\}$, including the empty set \varnothing\ and the total set $\gtotal$, and inclusion \textmorphisms $\iota: \opensetg_i \rightarrow \opensetg_j$.  
\end{definition}

To establish a mapping between graphic and data base spaces, we introduce the surjective map $\vindex: \gbase \rightarrow \dbase$. 
\begin{equation}
  \label{eq:artist:vindex}
  \begin{tikzcd}
    \dtotalc                        & \vindexc^*\dtotalc \arrow[l, "\vindexc^*"', dashed, color=artist]                                                                           \\
    \dbasec \arrow[u, "\dsectionc", color=section] & \gbasec \arrow[l, "\vindexc", color=artist] \arrow[lu, "\dsectionc \circ \vindexc" description, color=section] \arrow[u, "\vindexc^*\dsectionc"', dashed, color=section]
    \end{tikzcd}
\end{equation}
As shown in \autoref{eq:artist:vindex}, the map between spaces $\vindex$ can be composed with section map $\dsection$ such that there is a map from the graphic base space $\gbase$ to the fiber bundle in which the data lives $\dtotal$.

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindex^*}} \cgamma{\gbasec}{\vindexc^*\dtotalc}
\end{equation}
to generate a set of equivalent sections over the graphic $\Gamma(\gtotal, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \cgamma{\gbasec}{\vindexc^*{\dtotalc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

As with $\mathcal{\dbase}$, the morphisms between the open sets  $\opensetg$ are inclusion morphisms $\iota$. Over the graphic space $\opensetg \subseteq \gbase$ are a set of sections 
\begin{equation}
  \label{eq:artist:graphic_sections}
    \begin{split}
    \cgamma{\opensetgc}{\gtotalc|_{\opensetgc}} \coloneqq \{&\gsectionc^{0}, \cdots, \gsectionc^{i}, \cdots, \gsectionc^{n}\} \\
     &\gsectionc: \opensetgc\rightarrow \gtotalc|_{\opensetgc}
    \end{split}
  \end{equation}
\end{equation}
which are the set of all graphics with a shared base space and fiber and are a subcategory of \textbf{Set}. This allows us to represent the full space of graphics as a sheaf $\sheaf(\gtotal)$
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[row sep=huge]
    {\cgamma{\opensetgc}{\gtotalc|_{\opensetgc}}}&  & 
    \textcolor{set}{\{}\gsectionc:\opensetgc\rightarrow \gtotalc\textcolor{set}{\}}
    \arrow[ll, "\iota"', hook', color=set] \\ &  & \\
    \opensetgc \arrow[uu, "\sheafc(\gtotalc)", color=sheaf] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheafc_{\vartistc}(\gtotalc)" description, dashed, color=sheaf] &  & 
    \end{tikzcd}
\end{equation}
The set of graphics reachable through an artist function is a subset of sections of the full set of graphics $\{\gsection\} \subset \Gamma(\opensetg, \gtotal|_{\opensetg})$. These sets of reachable graphics over open sets \opensetg\ are also objects of \textbf{Set}. This allows us to formulate the graphic output by the artist as a sheaf 
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \sheafc_{\vartist}(\gtotalc): \gbasec^{\textcolor{base}{op}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}
from the graphic base space to the set of reachable graphics.

Following from \autoref{eq:artist:data_pullback_sheaf} and \autoref{eq:artist:artist_sheaf},  we propose that the artist function $\vartist$ is a natural transformation
\begin{equation}
  \label{eq:artist:natural-transform-diagram}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] & \\
\mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc_*}(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &  & {\setc}\\
    & {} &                            
\end{tikzcd}
\end{equation}

@@

which means that the artist can be pulled back through $\vindex^*$\footnote{Defintion 3.68 in Seven Sketches in Compositionality by Fong and Spivak}
\begin{equation}
  \begin{tikzcd}
    &                                                                                                                                                         & {} \arrow[dd, "\vartistc" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[r, "\vindexc^*", color=artist] & \mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindex^*}(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheaf_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &                                                    & \setc \\
    &                                                                                                                                                         & {}                                                 &      
\end{tikzcd}
\end{equation}
such that the artist can be constructed over data space 
\begin{equation}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc_{\vindexc^*}" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em,, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc^*}(\dtotalc)\circ\vindexc^* = \sheafc(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &                                                                 & \setc \\
    & {}                                                              &      
\end{tikzcd}
\end{equation}

>>>>

% *** MATH PACKAGES ***
%% with other math-related packages, you may want to disable it.
\usepackage{amsmath, amsthm, amsfonts,amssymb,eulervm,xspace, mathtools}
\usepackage{mathrsfs} % math script fonts
\usepackage{relsize} %bigger
\usepackage{bm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\newtheorem{example}{Example}[section]
% *** SPECIALIZED LIST PACKAGES ***
\usepackage{xcolor}
\usepackage{algorithmic}
\usepackage[utf8]{inputenc}
\usepackage{subfig} %ieee does not like subfigure
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?
\usepackage[switch]{lineno}
\renewcommand{\linenumberfont}{\normalfont\bfseries\small\color{lightgray}}
\usepackage{minted}
\setminted[python]{fontsize=\scriptsize, 
                   linenos,
                   numbersep=8pt,
                   autogobble, 
                   frame=lines,
                   framesep=3mm} 
% *** ALIGNMENT PACKAGES ***
\usepackage{array}
\usepackage{tabulary}
% IEEEtran contains the IEEEeqnarray family of commands

@@

\subsection{Sheaves}
\label{sec:related-work:continuity:sheaves}
Sheaves can be thought of as an "algebraic data structure" \cite{ghristElementaryAppliedTopology2014} for data that lives over topological spaces. A presheaf $\sheafc$ is a map from the open set to the set of sections $\sheafc: \opensetc \rightarrow \cgamma{\opensetc}{ \dtotalc|_{\opensetc}}$ \cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf}. The presheaf preserves inclusion maps $\iota$ between open sets and the inclusion map $\iota^*$ between the sets of sections.

@@

We introduce the category $\mathcal{\dbase}$ to encapsulate the continuity of the data, for example if the data are discrete points, continuous lines, images, or networks. 
\begin{definition} \label{def:category:K} The category of open sets $\mathcal{\dbasec}$ consists of
  \begin{itemize}
    \item \textit{objects} open sets $\openset_{i} \in \{\openset\}$ in the topological space $(\dbase, \mathscr{T})$), including the empty set $\varnothing$ and the maximum set \dbase. 
    \item \textit{morphisms} $\iota: \openset_{i} \hookrightarrow \openset_{j}$ for all  $\openset_i, \openset_j \subset \dtotal$
  \end{itemize} 
\end{definition}

We also introduce an analogous category $\mathcal{\gbase}$ that encapsulates the topology of the space in which the graphic is displayed, for example whether it is a 2D screen or a 3D printer.

\begin{definition} The category of open sets $\mathcal{\gbasec}$ in the topological space $(\dbase, \mathscr{T})$ consists of open set \textit{objects} $\opensetg \in \{\opensetg\}$, including the empty set $\varnothing$ and the maximum set $\gtotal$ and \textit{morphisms} $\iota: \opensetg_i \rightarrow \opensetg_j$.  
\end{definition}

The data space \dbase\ is a deformation retract of the graphic topology \gbase\
\begin{equation}
  \label{eq:artist:gbase}
  \gbase = \dbase \times I^{\text{dim}(display)-\text{dim}(\dbase)} 
\end{equation}
meaning that regions in \gbase\ collapse to points in \dbase\ such that the relative positions of the points are preserved \cite{nlab:deformation_retract}. The dimensionality of the data \dbase\ is expanded to match the dimensionality of the graphic display space by multiplying the data base space \dbase\ by intervals I.

\begin{figure}[h!]
  \label{fig:artist:gbase}
  \includegraphics[width=\columnwidth]{deform_retract.png}
  \caption{Given a 2D screen display, the graphic space \gbase\ must be 2D. It is constructed by multiplying the line \dbase\ by the interval [0,1] such that every vertical band in \gbase\ corresponds to a unique point $\dbasepoint \in \dbase$.}
\end{figure}

For example, as illustrated in \autoref{fig:artist:gbase}, the display space is a 2D screen and the data space is a 1D line \dbase. For that line to have any thickness, it must be rendered as a band. This means the region $(\dbasepoint, \alpha)|_{\alpha \in I} \subset \gbase$ maps to the corresponding point $\dbasepoint \in \dbase$.

\subsubsection{Data}
\note{clean up why sheaf}
As mentioned in \autoref{sec:related-work:continuity:sheaves}, sheaves are a powerful tool for keeping track of data that lies over topological spaces. Therefore, we model the type of data an artist expects as a sheaf $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$.
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc}{\dtotalc|_{\opensetc}} \in Ob(\setc) & \\
    {} & & {} \\
    & \opensetc \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)"', shift left = 10, color=sheaf] &   
\end{tikzcd}
\end{equation}
The objects of \textbf{Set} in this sheaf are the sets of sections $\Gamma(\dbase, \dtotal)$ introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps $(\iota, \iota^*)$ introduced in \autoref{eq:related-work:continuity:presheaf}.

To establish a mapping between graphic and data base spaces, we introduce the surjective map $\vindex: \gbase \rightarrow \dbase$. 
\begin{equation}
  \label{eq:artist:vindex}
  \begin{tikzcd}
    \dtotalc                        & \vindexc^*\dtotalc \arrow[l, "\vindexc^*"', dashed, color=artist]                                                                           \\
    \dbasec \arrow[u, "\dsectionc", color=section] & \gbasec \arrow[l, "\vindexc", color=artist] \arrow[lu, "\dsectionc \circ \vindexc" description, color=section] \arrow[u, "\vindexc^*\dsectionc"', dashed, color=section]
    \end{tikzcd}
\end{equation}
such that the data continuity $\dbase$ is a deformation retract of $\gbase$, as expressed in \autoref{eq:artist:gbase}.

As shown in \autoref{eq:artist:vindex}, the map between spaces $\vindex$ can be composed with section map $\dsection$ such that there is a map from the graphic base space $\gbase$ to the fiber bundle in which the data lives $\dtotal$.
\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindex^*}} \cgamma{\gbasec}{\vindexc^*\dtotalc}
\end{equation}
to generate a set of equivalent sections over the graphic space $\Gamma(\gbase, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \cgamma{\gbasec}{\vindexc^*{\dtotalc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

\subsubsection{Graphic}
We model the space of all graphic generating functions over a specific graphic topology $\opensetg \subseteq \gbase$ and targeting a specific display as a set of sections 
\begin{equation}
  \label{eq:artist:graphic_sections}
    \begin{split}
    \cgamma{\opensetgc}{\gtotalc|_{\opensetgc}} \coloneqq \{&\gsectionc^{0}, \cdots, \gsectionc^{i}, \cdots, \gsectionc^{n}\} \\
     &\gsectionc: \opensetgc\rightarrow \gtotalc|_{\opensetgc}
    \end{split}
  \end{equation}
\end{equation}
The set of sets of sections $\{\Gamma(\opensetg, \gtotal)\}|_{\opensetg \in gbase}$ is subcategory of \textbf{Set}; therefore the full space of graphics is a sheaf $\sheaf(\gtotal)$
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[row sep=huge]
    {\cgamma{\opensetgc}{\gtotalc|_{\opensetgc}}}&  & 
    \textcolor{set}{\{}\gsectionc:\opensetgc\rightarrow \gtotalc|_{\opensetgc}\textcolor{set}{\}}
    \arrow[ll, "\iota"', hook', color=set] \\ &  & \\
    \opensetgc \arrow[uu, "\sheafc(\gtotalc)", color=sheaf] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheafc_{\vartistc}(\gtotalc)" description, dashed, color=sheaf] &  & 
    \end{tikzcd}
\end{equation}

\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[column sep=tiny, row sep=huge]
    {\cgamma{\opensetgc}{\gtotalc|_{\opensetgc}}}&  & 
    \textcolor{set}{\{}\gsectionc:\opensetgc\rightarrow \gtotalc|_{\opensetgc}\textcolor{set}{\}}
    \arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\mathlarger{\supset}}}}" description, hook', color=white] \\ &  & \\
    \opensetgc \arrow[uu, "\sheafc(\gtotalc)", color=sheaf] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheafc_{\vartistc}(\gtotalc)" description, dashed, color=sheaf] &  & 
    \end{tikzcd}
\end{equation}

The set of graphics reachable through an artist function is a subset of sections of the full set of graphics $\{\gsection\} \subset \Gamma(\opensetg, \gtotal|_{\opensetg})$. These sets of reachable graphics over open sets \opensetg\ are also objects of \textbf{Set}. This allows us to formulate the graphic output by the artist as a sheaf 
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \sheafc_{\vartist}(\gtotalc): \gbasec^{\textcolor{base}{op}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}
from the graphic base space to the set of reachable graphics.

\subsubsection{Data to Graphic}
Following from \autoref{eq:artist:data_pullback_sheaf} and \autoref{eq:artist:artist_sheaf},  we propose that the artist function $\vartist$ is a natural transformation
\begin{equation}
  \label{eq:artist:natural-transform-diagram}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] & \\
\mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc_*}(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &  & {\setc}\\
    & {} &                            
\end{tikzcd}
\end{equation}

@@

which means that the artist can be pulled back through $\vindex^*$\footnote{Definition 3.68 in Seven Sketches in Compositionality by Fong and Spivak}
\begin{equation}
  \begin{tikzcd}
    &                                                                                                                                                         & {} \arrow[dd, "\vartistc" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[r, "\vindexc^*", color=artist] & \mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindex^*}(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheaf_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &                                                    & \setc \\
    &                                                                                                                                                         & {}                                                 &      
\end{tikzcd}
\end{equation}
such that the artist can be constructed over data space 
\begin{equation}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc_{\vindexc^*}" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em,, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc^*}(\dtotalc)\circ\vindexc^* = \sheafc(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &                                                                 & \setc \\
    & {}                                                              &      
\end{tikzcd}
\end{equation}
